---
title: "Survey Analysis - Using DANE HH Survey"
author: ""
date: ""
output: 
  html_document: 
    toc: yes
    number_sections: yes
---

DANE is among the fist National Statistical Office to systematically include a Migration Module within its Household survey. As explained in the report, [Nota Estadistica: Poblacion migrante venezolana panorama con enfoque de genero, jul 2021](https://reliefweb.int/sites/reliefweb.int/files/resources/jul-2021-nota-estadistica-poblacion-migrante-venezolana-panorama-con-enfoque-de-genero.pdf).

# Preparation Steps 

## Define Research Questions

* How is much the perceived current situation in comparison with the one 5 years ago differs between "Venezuelans without documentation" and other population? -> __Association Analysis__
* What can explain the reason for some "Venezuelans without documentation" to feel worst now than before? -> __Regression Analysis__
* What are the main profiles of "Venezuelans without documentation" that have a worst situation now than 5 years ago? -> __Clustering Analysis__


## Install packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
extrafont::loadfonts(quiet=TRUE)
# Turn off scientific notation
options(digits=3, scipen=8)

#  Packages             
if (!require("unhcRstyle")) remotes::install_github('unhcr-web/unhcRstyle')
if (!require("tidyverse")) install.packages("tidyverse", dependencies = TRUE)
if (!require("haven")) install.packages("haven", dependencies = TRUE)
if (!require("sjmisc")) install.packages("sjmisc", dependencies = TRUE)
if (!require("sjPlot")) install.packages("sjPlot", dependencies = TRUE)
if (!require("dplyr")) install.packages("dplyr", dependencies = TRUE)
if (!require("ggrepel")) install.packages("ggrepel", dependencies = TRUE)
if (!require("Hmisc")) install.packages("Hmisc", dependencies = TRUE)
if (!require("ggplot2")) install.packages("ggplot2", dependencies = TRUE)
if (!require("ggthemes")) install.packages("ggthemes", dependencies = TRUE)
if (!require("here")) install.packages("here", dependencies = TRUE)

library(tidyverse)
library(dplyr)
library(haven) 
library(sjlabelled)
library(sjmisc) 
library(sjPlot)
library(ggrepel)
library(Hmisc)
library(ggplot2)
library(ggthemes)
library(here)

#  Chart theme  
my_theme <-   theme_minimal(base_size = 8)  +
  theme(plot.title = element_text(hjust = 0.5, 
                              size = 14, 
                              color="red", 
                              face="bold.italic"),    # Center title position and size
        plot.subtitle = element_text(hjust = 0.5),            # Center subtitle
        plot.caption = element_text(hjust = 0, face = "italic"), # move caption to the left
        axis.title.x = element_text(color="blue", size=14, face="bold"),
        axis.title.y = element_text(color="#993333", size=14, face="bold")
  )
```

## Load Data

The dataset,  [Encuesta Nacional de Calidad de Vida ECV 2020, Colombia, DANE](http://microdatos.dane.gov.co/index.php/catalog/718/get_microdata) is available through a micro data library. Multiple labelled files shall first be merged together.

```{r cars}
# http://microdatos.dane.gov.co/index.php/catalog/718/get_microdata 
## Start with Household composition where disaggregation variables are
data0 <- haven::read_sav(here::here("data-raw", "Características y composición del hogar.sav"))
  
data1 <- haven::read_sav(here::here("data-raw", "Condiciones de vida del hogar y tenencia de bienes.sav"))
data <- dplyr::left_join(data0, data1, by = c("DIRECTORIO", "SECUENCIA_ENCUESTA", "SECUENCIA_P",       
                                              "ORDEN", "FEX_C" ) )

data2 <- haven::read_sav(here::here("data-raw", "Fuerza de trabajo.sav"))
data <- dplyr::left_join(data, data2, by = c("DIRECTORIO", "SECUENCIA_ENCUESTA", "SECUENCIA_P",       
                                              "ORDEN", "FEX_C" ) )

data3 <- haven::read_sav(here::here("data-raw", "Tenencia y financiación de la vivienda que ocupa el hogar.sav"))
data <- dplyr::left_join(data, data3, by = c("DIRECTORIO", "SECUENCIA_ENCUESTA", "SECUENCIA_P",       
                                              "ORDEN", "FEX_C" ) )

data4 <- haven::read_sav(here::here("data-raw", "Educación.sav"))
data <- dplyr::left_join(data, data4, by = c("DIRECTORIO", "SECUENCIA_ENCUESTA", "SECUENCIA_P",       
                                              "ORDEN", "FEX_C" ) )

data5 <- haven::read_sav(here::here("data-raw", "Salud.sav"))
data <- dplyr::left_join(data, data5, by = c("DIRECTORIO", "SECUENCIA_ENCUESTA", "SECUENCIA_P",       
                                              "ORDEN", "FEX_C" ) )

data6 <- haven::read_sav(here::here("data-raw", "Servicios del hogar.sav"))
data <- dplyr::left_join(data, data6, by = c("DIRECTORIO", "SECUENCIA_ENCUESTA", "SECUENCIA_P",       
                                              "ORDEN", "FEX_C" ) )

data7 <- haven::read_sav(here::here("data-raw", "Tecnologías de información y comunicación.sav"))
data <- dplyr::left_join(data, data7, by = c("DIRECTORIO", "SECUENCIA_ENCUESTA", "SECUENCIA_P",       
                                              "ORDEN", "FEX_C" ) )

rm(data0, data1, data2, data3, data4, data5, data6, data7)
 
## Display frame content
data %>% 
       sjPlot::view_df()
```

# Association Analysis 

> __Question__: How is much the perceived current situation in comparison with the one 5 years ago differs between "Venezuelans without documentation" and other population?

## Data Preparation
```{r prepare, echo= TRUE}
## let's create a variable for illegal (P1894 == 5) Venezualan (P756S3 == 3) -- 
data$IllegalVenez <- ifelse( (data$P1894 == 5 & data$P756S3 == 3), paste("Venz_SinDocumento"), paste("other"))
## Checking the merge
#table(data$IllegalVenez, useNA = "ifany")

# retrieve value and variable labels
#data.var <- sjlabelled::get_label(data)
data.val <-sjlabelled::get_labels(data)
weight <- as.vector(data$FEX_C)

cross <- c("IllegalVenez")
# set variable label for response
#set_label(data$IllegalVenez) <- "Venezuelan Sin Documento"
crosslab <- "Venezuelan Sin Documento"
```

## Plotting with Labels

```{r plot2, echo=TRUE, fig.height=7, fig.width=9}
i <- 55
var <- names(data)[i]
varlab <- sjlabelled::get_label(data[i])

sjPlot::plot_xtab(x= data[[i]],
                               grp = data[[cross]],
                               type = "bar",
                               weight.by = weight,
                               # sort.frq =  "asc",
                               # bar.pos = "stack",
                               wrap.labels = 40,
                               show.n = FALSE,
                               show.total = FALSE,
                               show.summary = TRUE,
                               show.prc = FALSE,
                               summary.pos = "r",
                               coord.flip = TRUE) +
        #unhcRstyle::unhcr_theme(base_size = 8)  + ## Insert UNHCR Style
        theme(#legend.position = "none",
              panel.grid.major.x  = element_line(color = "#cbcbcb"),
              panel.grid.major.y  = element_blank(),
              panel.grid.minor = element_blank()) + ### changing grid line that should appear
        ## and the chart labels
        labs(title = paste0(varlab),
             subtitle = paste0("Crossed with ", crosslab),
             x = "",
             y = "",
             caption = "Source: Encuesta Nacional de Calidad de Vida ECV 2020, Colombia, DANE")

```

# Regression analysis

> __Question__:  What can explain the reason for some "Venezuelans without documentation" to feel worst now than before?

## Data Preparation

```{r preparedata, echo= TRUE}
# levels(as.factor(data$P9050) )
# Usted piensa que el nivel de vida actual de su hogar, respecto al que tenía 5 años atrás es:
# create binary response
data$pejor <- ifelse(data$P9050 ==1, 0, 1)
# set variable label for response
set_label(data$pejor) <- "Pejor Nivel de Vida"

# create data frame for fitting model
df <- data[data$IllegalVenez =="Venz_SinDocumento", ## keep only illegal Venezuelan
           ## select potential explanatory variable
           c("pejor",
             "P6087", # el nivel de educación más alto el padre 
             "P2057", # ¿Usted se considera campesino(a)? 
             "P2059", # ¿Usted considera que alguna vez fue campesino(a)? 
             "P6020", # Sexo
             "P9010", # cómo se siente en el barrio
             "P1077S1", # Máquina lavadora de ropa 
             "P1077S2", # Nevera o refrigerador
             "P1077S3", # Estufa eléctrica o de gas
             "P1077S21", #Computador de escritorio 
             "P1075", #¿el hogar tiene conexión a internet?
             "P6250", #Además de lo anterior, ¿…..Realizó la semana pasada alguna actividad paga por una hora o más?
             "P6440", #¿Para realizar este trabajo tiene ….. algún tipode contrato?
             "P8634", #Fundamentalmente, donde realiza usted su trabajo principal:
             #"P400", "P403",
             "P9025S1") # Atracos o robos  
           ]
```

```{r  }
## Display frame content
df %>% 
       sjPlot::view_df()
```

## Logistic Regression

```{r plot3, echo= TRUE, fig.height=7, fig.width=9}
# fit model
m1 <- glm( pejor ~.,  ## explain  pejor
          data = df, 
          family = binomial(link = "logit") ## logistic regression
          )


sjPlot::plot_model(m1) +
       # unhcRstyle::unhcr_theme(base_size = 8)  + ## Insert UNHCR Style
        theme_minimal(base_size = 8) +
        theme(#legend.position = "none",
              panel.grid.major.x  = element_line(color = "#cbcbcb"),
              panel.grid.major.y  = element_blank(),
              panel.grid.minor = element_blank()) + ### changing grid line that should appear
        ## and the chart labels
        labs(title = "Pejor Nivel de Vida",
             subtitle = "",
            # x = "",
            # y = "",
             caption = "Source: Encuesta Nacional de Calidad de Vida ECV 2020, Colombia, DANE")

```


# Clustering analysis

> __Question__:  What are the main profiles of "Venezuelans without documentation" that have a worst situation now than 5 years ago?

## Methodology: an introduction to statistical clustering 

An important challenge to understand the profile of a population is to discover how categories interact together. To describe profiles within a population, it is necessary to interlace defined by multiple categories. Univariate analysis does not allow to get a synthetic vision from a large set of variables that can describe a population. Because of inherent brain & cognitive limitations, it is challenging to process together more than 7 categories and to make sense out of too many graphs.

Since the 70's, Social scientist have developed advanced __exploratory__ techniques that allow to discover statistical profiles among a specific population. Clustering is an exploratory data analysis tool wich aims to group a set of records in such a way that records in the same group are more similar to each other than to those in other groups. [Multiple Correspondence Analysis (MCA)](https://en.wikipedia.org/wiki/Multiple_correspondence_analysis) together with [Hierarchical Classification on Principle Components](http://factominer.free.fr/classical-methods/hierarchical-clustering-on-principal-components.html) allow to process nominal categorical data (as it is the case for Refugee biodata) in order to detect and represent the underlying structures in a data set. This approach is based on looking at description to generate induction rather than testing an hypothesis according to model.

This approach implies 5 simple steps:
 1. __Dimensionnality reduction__: Reduce the numbers of dimensions to two main composite dimensions in order to represent each observation in a 2D space.
 2. __Composition of the 2 axis__: Describe the components of each axis
 3. __Categories Representation__: This allow to visualise how close different variables are
 4. __Clustering__: Records are grouped according to profile using the underlying proximity between variables
 5. __Overview of groups__: Display the frequency of each group as well the breakdown of specific needs within each group.
 6. __Modalities within each group__: Describe the main variable modalities that describe the profile.

## Dimensionnality reduction 
Reduce the numbers of dimensions to two main composite dimensions in order to represent each observation in a 2D space.
The initial step is to first select the variable to use for the analysis. 

```{r preparedata2, echo= TRUE}

# create data frame for analysis
datacluster <- data[(data$IllegalVenez =="Venz_SinDocumento" &
                      data$pejor ==1), # # keep only illegal Venezuelan
         ## select potential explanatory variable
           c("P6087", # el nivel de educación más alto el padre 
             "P2057", # ¿Usted se considera campesino(a)? 
             "P2059", # ¿Usted considera que alguna vez fue campesino(a)? 
             "P6020", # Sexo
             "P9010", # cómo se siente en el barrio
             "P1077S1", # Máquina lavadora de ropa 
             "P1077S2", # Nevera o refrigerador
             "P1077S3", # Estufa eléctrica o de gas
             "P1077S21", #Computador de escritorio 
             "P1075") #¿el hogar tiene conexión a internet?)
           ]
```

```{r  }
## Display frame content
datacluster %>% 
       sjPlot::view_df()
```

```{r, echo=TRUE, warning=FALSE}
## Step : Check Frame
datacluster3 <- datacluster[complete.cases(datacluster), ]
if(nrow(datacluster3) > 10000) { samplesize <- 10000 } else { samplesize <- nrow(datacluster3)} 

data.sample <- as.data.frame(datacluster3[sample(1:nrow(datacluster3), samplesize, replace = FALSE), ] )
#summary(data.sample)
#str(data.sample)
``` 


```{r}

names(data.sample) <-  janitor::make_clean_names(label(data.sample), 
                                                       "small_camel")

data.sample <- data.sample %>% 
               lapply(. , factor) %>% 
               as.data.frame() %>%
               labelled::to_factor(., levels = "prefixed")

```

The algorithm is then used on those variable in order to assemble them within 2 dimensions. 

```{r, echo=TRUE, warning=FALSE, fig.height=7, fig.width=9}
 
# Dimensionality reduction: Multiple correspondance analysis
data.mca <- FactoMineR::MCA(data.sample, graph = FALSE)

factoextra::fviz_mca_ind(data.mca, 
                         col.ind = "blue", 
                         label = "none", 
                         addEllipses = TRUE, 
                         ellipse.level = 0.95, 
                         jitter = list(what = "point")) +
        theme_minimal(base_size = 8) +
  labs(title = "Geometric representation of Individuals in a cloud of points" )

```

## Composition of the 2 axis 
The graphs below describe the components within each of the dimensions from the previous representation. 

```{r, echo=TRUE, warning=FALSE}
## Contribution of top 10 variables
factoextra::fviz_contrib(data.mca, choice = "var", axes = 1, top = 15, sort.val = "asc") + 
        theme_minimal(base_size = 8) +
  labs(title = "Contribution of the top 15  variables to the first axis (Dim 1)", x = "", 
caption = "The reference dashed line corresponds to the expected value if the contribution where uniform")  +
  coord_flip()


factoextra::fviz_contrib(data.mca, choice = "var", axes = 2, top = 15, sort.val = "asc") + 
        theme_minimal(base_size = 8) +
  labs(title = "Contribution of the top 15  variables to the second axis (Dim 2)", x = "", 
caption = "The reference dashed line corresponds to the expected value if the contribution where uniform")  +
  coord_flip()
```

## Categories Representation  
It is also possible to map variable modalities on that bidimensional space. 
```{r, echo=TRUE, warning=FALSE}
factoextra::fviz_mca_var(data.mca, labelsize = 2, geom = "text", repel = TRUE, pointsize = 0, alpha.var = "contrib", palette = "RdBu", select.var = list(contrib = 20)) +
  labs(title = "Variable categories representation for the top 15 contributions" )  +
        theme_minimal(base_size = 8) 
```

## Hierarchical Classification  
We can now group together the observation based on their proximity. 

```{r, echo=TRUE, warning=FALSE}


## Predict projection for new rows with Multiple Correspondence Analysis
#data.predict <- predict(data.mca, data2)
#data.mca.hcpc <- FactoMineR::HCPC(data.mca, nb.clust = -1, min = 3, max = 4, graph = FALSE, order = FALSE, consol = TRUE, kk = 1000)


data.mca.hcpc <- FactoMineR::HCPC(data.mca, graph = FALSE)
# Visualize dendrogram
#factoextra::fviz_dend(data.mca.hcpc, show_labels = FALSE, rect = TRUE)
#factoextra::fviz_dend(data.mca.hcpc, cex = 0.5, k = 4,  color_labels_by_k = TRUE,  title="Hierarchical classification",  horiz=TRUE, rect = TRUE)


plot(data.mca.hcpc, 
     choice = "tree", 
     title = "Hierarchical classification",  
     horiz = TRUE, 
     tree.barplot = FALSE, 
     cex = 0.6)


plot(data.mca.hcpc, 
     title = "3D view within the cloud of point of the profiles")
plot(data.mca.hcpc, choice = "map", 
     title = "profiles within the cloud of points")


# Visualize cluster
#factoextra::fviz_cluster(data.mca.hcpc, ellipse.type = "convex")
#knitr::kable(data.mca.hcpc$desc.var$test.chi2, digits = 4, caption = "Ordered importance of variable contributions to profiles")


```


## Overview of groups  


 Once defined, we can now have an idea of the frequency of each profile. 

```{r, echo=TRUE, warning=FALSE}
cluster <- data.mca.hcpc$data.clust
cluster$clust <- as.character(cluster$clust)
cluster$clust[cluster$clust == 1] <- "Profile 1"
cluster$clust[cluster$clust == 2] <- "Profile 2"
cluster$clust[cluster$clust == 3] <- "Profile 3"
cluster$clust[cluster$clust == 4] <- "Profile 4"
cluster$clust[cluster$clust == 5] <- "Profile 5"
cluster$clust[cluster$clust == 6] <- "Profile 6"
cluster$clust <- as.factor(cluster$clust)


#names(cluster)


ggplot(cluster, aes(x = clust)) +
      geom_bar(aes(y = ..count.. / sapply(PANEL, FUN = function(x) sum(count[PANEL == x]))),
               fill = "#2a87c8", colour = "#2a87c8") +
      #facet_wrap(~subgov, ncol = 4) +
      guides(fill = FALSE) +
      ylab("Frequency") +
      scale_y_continuous(labels = scales::percent, breaks = seq(0, 1, by = 0.1)) +
      xlab("") +
      coord_flip() +
      ggtitle("Percentage of case per profile within the sample") +
  
      theme_minimal(base_size = 8) +
      theme(plot.title = element_text(face = "bold", size = 9),
            plot.background = element_rect(fill = "transparent",colour = NA)) 






```


## Modalities within each group  
Describe the main variable modalities that describe the profile.

The variable modalities in each of the profiles can be __interpreted__ using the following information: 

 * _Cla/Mod_ is the percentage of records who have that modality and who are in that the profile (for instance: 50.3% of the cases who have a head of family who marital status is single also belongs to profile 1)


 * _Mod/Cla_ is the percentage of records in that profile who have that modality (for instance: 81.5% of the cases of profile  1 have a head of family who marital status is single )


 * _Global_ is the global percentage of all records who have that modality (for instance: in all population, 51.67% of of the cases who have a head of family who marrital status is single.)


 * _p-value_ provides an idea of the significant of the difference between Mod/Cla proportion & Global. If p-value is less than 0.05, then one category is significantly linked to another categories 


 * _v-test_ If the v-test is positive, it means that the category is over-expressed for the category and if the v-test is negative it means that the category is under-expressed for the category.What is interesting in the v-test is only the sign of the v-test.


Only variable modalities for which critical probability is below 0.02 are used.
 The graph below allows to describe each profile in narrative terms. 

```{r, echo=TRUE, warning=FALSE}

#knitr::kable(data.mca.hcpc$desc.var$category$`1`, digits = 2, caption = "Description of modalities contribution to Profile 1") 
t1 <- as.data.frame(data.mca.hcpc$desc.var$category$`1`)
names(t1) <-  janitor::make_clean_names(names(t1),  "small_camel")
#names(t1)
t1$measure <- sub(".*=", "", row.names(t1)) 
t1$Expression <- as.factor(ifelse(t1$vTest >0 , "Over-expressed", "Under-expressed"))
t1$Linkage <- as.factor(ifelse(t1$pValue < 0.05 , "Linked", "Independant"))

ggplot(t1) +
  #geom_col(aes(measure, claMod, fill = "claMod"), width=0.5, alpha=0.2) +
  geom_col(aes(measure, modCla, fill = "modCla"), width=0.4, alpha=0.3) +
  geom_col(aes(measure, global, fill = "global"), width=0.8, alpha=0.3) + 
  scale_fill_manual(name = "Legend",
                    values = c(#"claMod" = "goldenrod2", 
                               "modCla" = "goldenrod4", 
                               "global" = "goldenrod2"),
                    breaks = c(#"claMod", 
                      "modCla", "global")) +       
  geom_point(aes(measure, claMod, 
                 color = Expression,
                 shape = Linkage),   size=2.5) +
  coord_flip()+
  theme_bw() + 
  theme(
    plot.title = element_text(face = "bold", size = 12),
    legend.background = element_rect(fill = "white", size = 4, colour = "white"),
    #legend.justification = c(0, 1),
    #legend.position = c(0, 1),
    legend.position="bottom",
    legend.title = element_blank(),
    axis.ticks = element_line(colour = "grey70", size = 0.2),
    panel.grid.major = element_line(colour = "grey70", size = 0.2),
    panel.grid.minor = element_blank()
  ) + 
   labs(title = "Description of modalities contribution to Profile 1",
     subtitle = str_wrap("Interpretation hint: \n Cla/Mod, represented as a point is the percentage of records who have that modality and who are in that the profile.\n
     Mod/Cla is the percentage of records in that profile who have that modality, while  Global is the global percentage of all records who have that modality", 150),
     x = "",
     y = "Percent",
     caption = "")



#knitr::kable(data.mca.hcpc$desc.var$category$`2`, digits = 2, caption = "Description of modalities contribution to Profile 2")
t2 <- as.data.frame(data.mca.hcpc$desc.var$category$`2`)
names(t2) <-  janitor::make_clean_names(names(t2),  "small_camel")
#names(t2)
t2$measure <- sub(".*=", "", row.names(t2)) 
t2$Expression <- as.factor(ifelse(t2$vTest >0 , "Over-expressed", "Under-expressed"))
t2$Linkage <- as.factor(ifelse(t2$pValue < 0.05 , "Linked", "Independant"))

ggplot(t2) +
  #geom_col(aes(measure, claMod, fill = "claMod"), width=0.5, alpha=0.2) +
  geom_col(aes(measure, modCla, fill = "modCla"), width=0.4, alpha=0.3) +
  geom_col(aes(measure, global, fill = "global"), width=0.8, alpha=0.3) + 
  scale_fill_manual(name = "Legend",
                    values = c(#"claMod" = "goldenrod2", 
                               "modCla" = "goldenrod4", 
                               "global" = "goldenrod2"),
                    breaks = c(#"claMod", 
                      "modCla", "global")) +       
  geom_point(aes(measure, claMod, 
                 color = Expression,
                 shape = Linkage),   size=2.5) +
  coord_flip()+
  theme_bw() + 
  theme(
    plot.title = element_text(face = "bold", size = 12),
    legend.background = element_rect(fill = "white", size = 4, colour = "white"),
    #legend.justification = c(0, 1),
    #legend.position = c(0, 1),
    legend.position="bottom",
    legend.title = element_blank(),
    axis.ticks = element_line(colour = "grey70", size = 0.2),
    panel.grid.major = element_line(colour = "grey70", size = 0.2),
    panel.grid.minor = element_blank()
  ) + 
   labs(title = "Description of modalities contribution to Profile 2",
     subtitle = str_wrap("Interpretation hint: \n Cla/Mod, represented as a point is the percentage of records who have that modality and who are in that the profile.\n
     Mod/Cla is the percentage of records in that profile who have that modality, while  Global is the global percentage of all records who have that modality", 150),
     x = "",
     y = "Percent",
     caption = "")



#knitr::kable(data.mca.hcpc$desc.var$category$`3`, digits = 2, caption = "Description of modalities contribution to Profile 3")
t3 <- as.data.frame(data.mca.hcpc$desc.var$category$`3`)
names(t3) <-  janitor::make_clean_names(names(t3),  "small_camel")
#names(t3)
t3$measure <- sub(".*=", "", row.names(t3)) 
t3$Expression <- as.factor(ifelse(t3$vTest >0 , "Over-expressed", "Under-expressed"))
t3$Linkage <- as.factor(ifelse(t3$pValue < 0.05 , "Linked", "Independant"))

ggplot(t3) +
  #geom_col(aes(measure, claMod, fill = "claMod"), width=0.5, alpha=0.2) +
  geom_col(aes(measure, modCla, fill = "modCla"), width=0.4, alpha=0.3) +
  geom_col(aes(measure, global, fill = "global"), width=0.8, alpha=0.3) + 
  scale_fill_manual(name = "Legend",
                    values = c(#"claMod" = "goldenrod2", 
                               "modCla" = "goldenrod4", 
                               "global" = "goldenrod2"),
                    breaks = c(#"claMod", 
                      "modCla", "global")) +       
  geom_point(aes(measure, claMod, 
                 color = Expression,
                 shape = Linkage),   size=2.5) +
  coord_flip()+
  theme_bw() + 
  theme(
    plot.title = element_text(face = "bold", size = 12),
    legend.background = element_rect(fill = "white", size = 4, colour = "white"),
    #legend.justification = c(0, 1),
    #legend.position = c(0, 1),
    legend.position="bottom",
    legend.title = element_blank(),
    axis.ticks = element_line(colour = "grey70", size = 0.2),
    panel.grid.major = element_line(colour = "grey70", size = 0.2),
    panel.grid.minor = element_blank()
  ) + 
   labs(title = "Description of modalities contribution to Profile 3",
     subtitle = str_wrap("Interpretation hint: \n Cla/Mod, represented as a point is the percentage of records who have that modality and who are in that the profile.\n
     Mod/Cla is the percentage of records in that profile who have that modality, while  Global is the global percentage of all records who have that modality", 150),
     x = "",
     y = "Percent",
     caption = "")



#knitr::kable(data.mca.hcpc$desc.var$category$`4`, digits = 2, caption = "Description of modalities contribution to Profile 4")
t4 <- as.data.frame(data.mca.hcpc$desc.var$category$`4`)
names(t4) <-  janitor::make_clean_names(names(t4),  "small_camel")
#names(t4)
t4$measure <- sub(".*=", "", row.names(t4)) 
t4$Expression <- as.factor(ifelse(t4$vTest >0 , "Over-expressed", "Under-expressed"))
t4$Linkage <- as.factor(ifelse(t4$pValue < 0.05 , "Linked", "Independant"))

ggplot(t4) +
  #geom_col(aes(measure, claMod, fill = "claMod"), width=0.5, alpha=0.2) +
  geom_col(aes(measure, modCla, fill = "modCla"), width=0.4, alpha=0.3) +
  geom_col(aes(measure, global, fill = "global"), width=0.8, alpha=0.3) + 
  scale_fill_manual(name = "Legend",
                    values = c(#"claMod" = "goldenrod2", 
                               "modCla" = "goldenrod4", 
                               "global" = "goldenrod2"),
                    breaks = c(#"claMod", 
                      "modCla", "global")) +       
  geom_point(aes(measure, claMod, 
                 color = Expression,
                 shape = Linkage),   size=2.5) +
  coord_flip()+
  theme_bw() + 
  theme(
    plot.title = element_text(face = "bold", size = 12),
    legend.background = element_rect(fill = "white", size = 4, colour = "white"),
    #legend.justification = c(0, 1),
    #legend.position = c(0, 1),
    legend.position="bottom",
    legend.title = element_blank(),
    axis.ticks = element_line(colour = "grey70", size = 0.2),
    panel.grid.major = element_line(colour = "grey70", size = 0.2),
    panel.grid.minor = element_blank()
  ) + 
   labs(title = "Description of modalities contribution to Profile 4",
     subtitle = str_wrap("Interpretation hint: \n Cla/Mod, represented as a point is the percentage of records who have that modality and who are in that the profile.\n
     Mod/Cla is the percentage of records in that profile who have that modality, while  Global is the global percentage of all records who have that modality", 150),
     x = "",
     y = "Percent",
     caption = "")


#knitr::kable(data.mca.hcpc$desc.var$category$`5`, digits = 2, caption = "Description of modalities contribution to Profile 5")
# t1 <- as.data.frame(data.mca.hcpc$desc.var$category$`1`)
# names(t1) <-  janitor::make_clean_names(names(t1),  "small_camel")
# names(t1)
# t1$measure <- row.names(t1)
# t1$expressed <- as.factor(ifelse(t1$vTest >0 , "over-expressed", "under-expressed"))
# t1$linked <- as.factor(ifelse(t1$pValue < 0.05 , "linked", "independant"))
# 
# ggplot(t1) +
#   #geom_col(aes(measure, claMod, fill = "claMod"), width=0.5, alpha=0.2) +
#   geom_col(aes(measure, modCla, fill = "modCla"), width=0.4, alpha=0.3) +
#   geom_col(aes(measure, global, fill = "global"), width=0.8, alpha=0.3) + 
#   scale_fill_manual(name = "Legend",
#                     values = c(#"claMod" = "goldenrod2", 
#                                "modCla" = "goldenrod4", 
#                                "global" = "goldenrod2"),
#                     breaks = c(#"claMod", 
#                       "modCla", "global")) +       
#   geom_point(aes(measure, claMod, 
#                  color = expressed,
#                  shape = linked),   size=2.5) +
#   coord_flip()+
#   theme_bw() + 
#   theme(
#     plot.title = element_text(face = "bold", size = 12),
#     legend.background = element_rect(fill = "white", size = 4, colour = "white"),
#     #legend.justification = c(0, 1),
#     #legend.position = c(0, 1),
#     axis.ticks = element_line(colour = "grey70", size = 0.2),
#     panel.grid.major = element_line(colour = "grey70", size = 0.2),
#     panel.grid.minor = element_blank()
#   ) + 
#    labs(title = "Description of modalities contribution to Profile 1",
#      subtitle = "Interpretation hint: \n Cla/Mod, represented as a point is the percentage of records who have that modality and who are in that the profile.\n
#      Mod/Cla is the percentage of records in that profile who have that modality, while  Global is the global percentage of all records who have that modality",
#      # x = "",
#      # y = "",
#      caption = "")



```


__Reference__: [hierarchical-clustering-on-principal-components](http://www.sthda.com/english/wiki/hcpc-hierarchical-clustering-on-principal-components-hybrid-approach-2-2-unsupervised-machine-learning).


